Species with high control capacity support stable coexistence of pollination networks

### 2018-07-19 paper/cover-letter.tex
Also thank the assistant editor

We are thankful to the senior and associate editors, Prof.\ David Gibson and Prof.\ Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
We are also grateful for the opportunity to resubmit.

>>>>

We are thankful to the assistant editor James Ross, the editors Prof.\ Nicole Rafferty and Prof.\ David Gibson, and two anonymous reviewers for the insightful comments to improve the manuscript. 
We are also grateful for the opportunity to resubmit.
